Uncertainty on the galaxy-halo connection for Lyman-$\alpha$ emitters at $z=3.1$

### 2016-03-30 paper/ms.tex
new caption for fig5
recent bolshoi references

\begin{figure}
\includegraphics[width=0.50\textwidth]{fig1.pdf}
\caption{Cumulative halo number density distribution function over
  27 mock fields. Each line corresponds to a
  different model with increasig values of $M_{\rm min}$. 
  Different models produce different number density distributions. The
width increases with \mmin.} 
\label{fig:cosmicv0}
\end{figure}

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.85\textwidth]{likelyplot_1deg_total.png}
\end{center}
\caption{One and two dimensional projections of the posterior
  probability distributions of \mmin, \mmax\ and \focc\ as described in
  the label of each sub-figure. We remark that
those models where $\log \focc>0.00$ ($\focc>1$) correspond  to models where the number density  of halos is smaller than the number of observed LAEs but are
still consistent because of the uncertainty in the median number
density of LAEs in the universe due to cosmic variance. See
Fig. \ref{fig:cosmicv0} and \S\ref{subsec:explore} for details.} 
\label{fig:like}
\end{figure*}

@@

We use results from the  Bolshoi simulation \citep{Bolshoi} which was performed in a cubic volume of 250 $h^{-1}$ Mpc comoving on a side. The dark matter distribution was sampled using  $2048^{3}$ particles. The cosmological parameters are consistent with Planck 2013 results \citep{Planck2014} with a matter density
$\Omega_{\rm m} = 0.307$, cosmological constant
$\Omega_{\Lambda}=0.693$, dimensionless Hubble constant $h=0.70$, slope
of the power spectrum  $n=0.96$ and normalization of the power
spectrum $\sigma_{8}=0.82$.  
This translates into a particle mass of  $m_{\rm p}=1.54\times 10^{8}$ $h^{-1}$ M$_{\odot}$.

We use halo catalogs constructed with a Bound-Density-Maxima (BDM) algorithm. The catalogs were obtained from the publicly available
Multidark database  \footnote{{\tt
    http://www.multidark.org/MultiDark/}} \citep{MultiDark}. For each
halo in the box we extract its comoving position and mass. 
We focus our work on halos more massive than $1.54\times 10^{9}$\hMsun\ resolved with at least  $10$ particles.
%the reasons for this choice are explained in the next sub-section.

We divide the total volume of the snapshot of the simulation at z$\sim$3
into  27 smaller mock volumes mimicking the  comoving area and depth  
reported in \citet{Bielby16} and described in \S \ref{subsec:obs}. 
This allows  us to take explicitly into account the effects of cosmic variance.

@@

\includegraphics[width=0.47\textwidth]{corr.png}
\caption{ Angular Correlation functions for $\log M_{\rm min}[\rm{M_{\odot}h^{-1}}]=10.5$ and different values of $\Delta M$. The error bars represent the 1 sigma deviation due to cosmic variance.}
\label{fig:corr}
\end{figure}

@@

>>>>

\begin{figure}
\includegraphics[width=0.47\textwidth]{fig1.pdf}
\caption{Cumulative halo number density distribution function over
  27 mock fields. Each line corresponds to a
  different model with increasig values of $M_{\rm min}$. 
  Different models produce different number density distributions. The
width increases with \mmin. } 
\label{fig:cosmicv0}
\end{figure}

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.85\textwidth]{likelyplot_1deg_total.png}
\end{center}
\caption{One and two dimensional projections of the posterior
  probability distributions of \mmin, \mmax\ and \focc\. 
  The models with $\log \focc>0.00$ ($\focc>1$) correspond  to models
  where the number density  of halos is smaller than the number of
  observed LAEs but we consider them as consistent because of the uncertainty
  in the median number density due to cosmic variance. See 
Fig. \ref{fig:cosmicv0} and \S\ref{subsec:explore} for details.} 
\label{fig:like}
\end{figure*}

@@

We use results from the Bolshoi simulation \citep{Bolshoi,BolshoiP} which was
performed in a cubic volume of 250 $h^{-1}$ Mpc comoving on a side. 
The dark matter distribution was sampled using  $2048^{3}$
particles. 
The cosmological parameters are consistent with Planck
results \citep{Planck2014} with a matter density 
$\Omega_{\rm m} = 0.307$, cosmological constant
$\Omega_{\Lambda}=0.693$, dimensionless Hubble constant $h=0.678$, slope
of the power spectrum  $n=0.96$ and normalization of the power
spectrum $\sigma_{8}=0.823$.  
This translates into a particle mass of  $m_{\rm p}=1.5\times 10^{8}$
$h^{-1}$ M$_{\odot}$.

We use halo catalogs constructed with a Bound-Density-Maxima (BDM)
algorithm. 
The catalogs were obtained from the publicly available Multidark
database  \footnote{\url{http://www.multidark.org/MultiDark/}}
\citep{MultiDark}. 
For each  halo in the box we extract its comoving position and mass.  
We focus our work on halos more massive than $1.5\times
10^{9}$\hMsun\ resolved with at least  $10$ particles.

We split the simulation volume at z$\sim$3 into  27 smaller mock
volumes mimicking the  area and depth reported in \citet{Bielby16} and
described in \S \ref{subsec:obs}.

@@

  \includegraphics[width=0.47\textwidth]{fig5.pdf}
\caption{ Angular Correlation functions for $\log M_{\rm
    min}[\rm{M_{\odot}h^{-1}}]=10.5$ and different values of $\Delta
  M$.  
  The shaded region represents the 1-sigma deviation due to cosmic
  variance. Radical different models in $\Delta M$ are consistent with
  observations once cosmic variance is modelled in detail.}
\label{fig:corr}
\end{figure}

@@

The authors gratefully acknowledge the Gauss Centre for Supercomputing
e.V. (\url{www.gauss-centre.eu}) and the Partnership for Advanced
Supercomputing in Europe (PRACE, \url{www.prace-ri.eu}) for funding the
MultiDark simulation project by providing computing time on the GCS
Supercomputer SuperMUC at Leibniz Supercomputing Centre (LRZ,
\url{www.lrz.de}). The Bolshoi simulations have been performed within the
Bolshoi project of the University of California High-Performance
AstroComputing Center (UC-HiPACC) and were run at the NASA Ames
Research Center.
